---
title: "Results report: Outliers in Bean data"
author: "Anitha Pai"
output: html_document
---

Display boxplots to display outliers in each column of the bean data

```{r setup,include=FALSE,message=FALSE}
library(drake)
library(gridExtra)
```

Abstract: Images of 13,611 grains of 7 different registered dry beans were taken with a high-resolution camera. A total of 16 features; 12 dimensions and 4 shape forms, were obtained from the grains.Sample data displayed below

```{r data,echo=FALSE,message=FALSE}
readd(display_bean)
```

which of these variables are integers and pass the Shapiro test for Normality.

```{r data2,echo=FALSE,message=FALSE}
readd(is_it_normal_colnames)
```


Plot the normality and qq plots for all such columns

```{r, figures-side, fig.show="hold", out.width="50%",echo=FALSE,message=FALSE}

loadd(plot1)
loadd(plot2)

par(mar = c(4, 4, .1, .1))
plot(plot1)
plot(plot2)
```


Now, these columns go through Rosner test to be checked for outliers.Plot these columns and display their outliers via boxplots

```{r, fig.show="hold",echo=FALSE,message=FALSE}

loadd(plot3)
plot(plot3)
```
